### 2024-07-08 basic-statistics.qmd
20240708 - weighted mean, weighted median (or other quantile)

- mean
- median
- Hodges-Lehmann statistic (aka pseudomedian)
- mode

@@

@@

>>>>

- mean
- median
- Hodges-Lehmann statistic (aka pseudomedian)
- mode
- weighted mean
- weighted median

@@

If you want to give some values more weight to others, you can calculate a weighted mean and a weighted median (or other quantile), while assigning a weight to each value.

@@

```{r}
#mean(data, na.rm = TRUE)
#median(data, na.rm = TRUE)
#DescTools::HodgesLehmann(exampleValues, na.rm = TRUE)
#petersenlab::Mode(exampleValues)
#weighted.mean(data, weights, na.rm = TRUE)
#DescTools::Quantile(data, weights, na.rm = TRUE)
```
